Towards Language Model-based Identification of Market Segments and Fostering of Business Clusters

### 2023-06-19 paper/report.tex
add comments

@@

However, the identification of market segments, and moreover that of business clusters, is complicated by the fact that data on regional companies is often unavailable or difficult to analyze due to non-numerical, irrelevant, or missing features.

@@

Our location recommendation system builds upon the clustering pipeline by computing an embedding of a novel company's description, assigning it to a cluster, and then identifying the most similar companies within the cluster. The system then recommends that the novel company locate its site near an established company acting in the same market segment, which fosters business cluster development in Saarland.

@@

\subsection{Identifying Market Segments through Clustering}
Figure \hyperref{fig:pipeline}{$1$} shows a graphical representation of our clustering pipeline, consisting of $4$ steps: $1)$ Collection of descriptions from company websites, $2)$ converting the descriptions to embeddings, $3)$ reducing the dimensionality of the embeddings, and $4)$ applying a clustering algorithm. In the following, we will examine each of these steps in detail.

\textit{$1)$ Collect Descriptions:} Given that high-quality economic data is highly valuable, there are no freely available data sets we could rely on for our purposes, meaning we need to build our dataset from scratch. The traditional approach for building such a dataset would be to gather several attributes, like revenue, number of employers, and products, for many companies in Saarland and then store each in a fixed-size vector. However, this approach has several drawbacks: It is not straightforward to encode non-numerical attributes, like products and customer base, such that clustering algorithms can parse them without introducing an unwanted ordering of the attributes' values. Further, some attributes may be unavailable for some companies, meaning we would need to discard them because we require fixed-size vectors, or we would need to insert dummy values, which could lead to unwanted effects. Lastly, representing a company using a small number of publicly available attributes might be insufficient for capturing all relevant characteristics. For instance, consider the smartphone manufacturers Apple and Samsung: Both companies build smartphones, have over $100.000$ employees, have revenues of over $200$ billion dollars, and have production and sales sites worldwide. Given these attributes, one could argue that Apple and Samsung are very similar companies. Yet, it is commonly known that Apple, with its minimalist design, high-end smartphones targeted toward customers looking to differentiate themselves from other people, and Samsung, with its more utilitarian smartphones targeted toward a broad customer base, are companies with fundamentally different characters.
To address these challenges to dataset construction, we propose representing companies by the description on their websites instead of numerical attributes. Since companies want to present themselves publicly in a way that attracts customers and investors, these descriptions contain the information needed to represent them accurately.

>>>>

% TODO commands package
\usepackage{todonotes}
\newcommand{\pe}[1]{\todo[inline, backgroundcolor=green]{PE: #1}}

@@

\pe{I find the claims made in this paragraph to be to not backed by evidence. While I have no economic background, I was able to source some existing literature, e.g. \href{http://biblioteca.fundacionicbc.edu.ar/images/d/de/Clusters_1.pdf}{1}, \href{https://onlinelibrary.wiley.com/doi/full/10.1111/j.1536-7150.2011.00819.x}{2},
\href{https://www.jstor.org/stable/144358?seq=1}{3}, \href{https://www.emerald.com/insight/content/doi/10.1108/14715200280001472/full/pdf?title=cluster-theory-and-practice-advantages-for-the-small-business-locating-in-a-vibrant-cluster}{4}. Feel free to add the standard literature / different sources}

However, the identification of market segments, and moreover that of business clusters, is complicated by the fact that data on regional companies is often unavailable or difficult to analyze due to non-numerical, irrelevant, or missing features.
\pe{This seems a harsh claim, in practice one could argue that it is available through regional connections}

@@

Our location recommendation system builds upon the clustering pipeline by computing an embedding of a novel company's description, assigning it to a cluster, and then identifying the most similar companies within the cluster. The system then recommends that the novel company locate its site near an established company acting in the same market segment, which fosters business cluster development in Saarland.
\pe{I have yet to find a backing for this approach, feel free to help me out here}

@@

\subsection{Identifying Market Segments through Clustering}
Figure \ref{fig:pipeline} shows a graphical representation of our clustering pipeline, consisting of $4$ steps: $1)$ Collection of descriptions from company websites, $2)$ converting the descriptions to embeddings, $3)$ reducing the dimensionality of the embeddings, and $4)$ applying a clustering algorithm. In the following, we will examine each of these steps in detail.

\textit{$1)$ Collect Descriptions:} Given that high-quality economic data is highly valuable, there are no freely available data sets we could rely on for our purposes, meaning we need to build our dataset from scratch. \pe{TODO: rephrase} The traditional approach for building such a dataset would be to gather several attributes, like revenue, number of employers, and products, for many companies in Saarland and then store each in a fixed-size vector. \pe{TODO: backup with accepted approach} However, this approach has several drawbacks: It is not straightforward to encode non-numerical attributes, like products and customer base, such that clustering algorithms can parse them without introducing an unwanted ordering of the attributes' values. Further, some attributes may be unavailable for some companies, meaning we would need to discard them because we require fixed-size vectors, or we would need to insert dummy values, which could lead to unwanted effects. Lastly, representing a company using a small number of publicly available attributes might be insufficient for capturing all relevant characteristics. For instance, consider the smartphone manufacturers Apple and Samsung: Both companies build smartphones, have over $100.000$ employees, have revenues of over $200$ billion dollars, and have production and sales sites worldwide. Given these attributes, one could argue that Apple and Samsung are very similar companies. Yet, it is commonly known that Apple, with its minimalist design, high-end smartphones targeted toward customers looking to differentiate themselves from other people, and Samsung, with its more utilitarian smartphones targeted toward a broad customer base, are companies with fundamentally different characters.
To address these challenges to dataset construction, we propose representing companies by the description on their websites instead of numerical attributes. Since companies want to present themselves publicly in a way that attracts customers and investors, these descriptions contain the information needed to represent them accurately.
